Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Fixed cite commands to citet and citep, removed tildes

\begin{defn}
  A measure of the ease of installation.  \wss{Where does this definition come
    from? Please add a citation.}
\end{defn}

\begin{defn} \label{DefnInstallability}
  Installability is related to the amount of human effort required to install a
  software in a designated environment \cite{berander2005software}.
\end{defn}

\begin{defn}
  ``The capability of a software product to be installed in a specified
  environment'' \cite{berander2005software}.
\end{defn}

\begin{defn}
  ``The efficacy of the installation, uninstallation or reinstallation process
  of a software product in a specified environment'' (\cite{iso201017043})
\end{defn}

@@

The quality of a software's operation is dependent on the degree of correctness
\cite{berander2005software}. Correctness and reliability are said to have
dependencies, such that if a system exhibits a high degree of correctness then
it tends to be reliable (\cite{GhezziEtAl2003}).

@@

\begin{defn}
  A software is verifiable if its properties can be verified
  (\cite{GhezziEtAl2003}).
\end{defn}

\begin{defn}
  Attributes of software that relate to the effort needed for validating the
  modified software (\cite{berander2005software}).
\end{defn}

\begin{defn}
  The degree to which a system or component facilitates the establishment of
  test criteria and the performance of tests to determine whether those criteria
  have been met (\cite{IEEEStdGlossarySET1990}).
\end{defn}

\begin{defn} \label{Defn_Verifiability1}
  The degree to which a requirement is stated in terms that permit establishment
  of test criteria and performance (\cite{IEEEStdGlossarySET1990}).
\end{defn}

\begin{defn} \label{Defn_Verifiability2}
  Ease of performing testing on a software product or system
  (\cite{IEEEStdGlossarySET1990}).
\end{defn}

@@

Verifiability involves ``solving the equations right''~\cite[p.~23]{Roache1998};
it benefits from rational documentation that systematically shows, with explicit
traceability, how the governing equations are transformed into code.
\oo{Verifiability is sometimes referred to as testability, so I culled some
  testability definitions here}

@@

\begin{defn}
  Validatability means ``solving the right equations''~\cite[p.~23]{Roache1998}.
  \oo{question about this definition}
\end{defn}

@@

\begin{defn}
  The probability that the software will operate as expected over a specified
  time interval (\cite{GhezziEtAl2003}).
\end{defn}

\begin{defn}
  A set of attributes that relate to the capability of software to maintain its
  level of performance under stated conditions for a stated period of time
  (\cite{berander2005software}).
\end{defn}

\begin{defn}
  ``The capability of the software product to maintain a specified level of
  performance when used under specified conditions''
  (\cite{international2001iso}).
\end{defn}

\begin{defn}
  Code possesses the characteristic reliability to the extent that it can be
  expected to perform its intended functions satisfactorily
  (\cite{boehm2007software}).
\end{defn}

\begin{defn}
  A concern encompassing correctness and robustness (\cite{meyer1988object}).
\end{defn}

@@

Reliability models can be used to predict reliability of a software product. For
example measuring Mean Time to Fail (MTTF) can be a good measure of reliability
\cite{berander2005software}.

@@

One core reference, for definitions and metrics, is Bevan~\cite{bevan1995measuring}.

@@

Section 11.2 of~\cite{adams2015nonfunctional} does have a full definition.

@@

Reproducibility is a required component of the scientific
method~\cite{Davison2012}.  Although QA has, ``a bad name among creative
scientists and engineers''~\cite[p.~352]{Roache1998}, the community need to
recognize that participating in QA management also improves reproducibility.
Reproducibility, like QA, benefits from a consistent and repeatable computing
environment, version control and separating code from
configuration/parameters~\cite{Davison2012}.

@@

\begin{defn}
\noindent The ability to meet the needs of the present without compromising the ability of
future generations to meet their own needs \cite{Brundtland1987}.
\end{defn}

This is the definition used by~\cite{IISD2019}.

To make it more useful, this definition is often split into three dimensions:
social, economic and environmental. \wss{cite UN paper [9] in
  \cite{PenzenstadlerAndHenning2013}}  To this list Penzenstadler and Henning
(2013) have added technical sustainability \cite{PenzenstadlerAndHenning2013}.
Where technical sustainability for software is defined as:

\begin{defn}
\noindent Technical sustainability has the central objective of long-time
usage of systems and their adequate evolution with changing surrounding
conditions and respective requirements \cite{PenzenstadlerAndHenning2013}.
\end{defn}

The fourth dimension of technical sustainability is also added
by~\cite{WolframEtAl2017}.  Technical sustainability is the focus on the thesis
by~\cite{Hygerth2016}.

\begin{defn}
  \noindent Sustainable development is a mindset (principles) and an
  accompanying set of practices that enable a team to achieve and maintain an
  optimal development pace indefinitely~\cite{Tate2005}.
\end{defn}

Parnas discusses as software aging~\cite{Parnas1994a}.

@@

\begin{defn}
  The concept of sustainability is based on three pillars: the
  ecological, the economical and the social. This means that for a software to
  be sustainable, we must take all of its effects -- direct and indirect -- on
  the environment, the economy and the society into account. In addition, the
  entire life cycle of a software has to be considered: from planning and
  conception to programming, distribution, installation, usage and
  disposal~\cite{Heine2017}.
\end{defn}

\begin{defn}
  \noindent The capacity of the software to endure. In other words,
  sustainability means that the software will continue to be available in the
  future, on new platforms, meeting new needs~\cite{Katz2016}.
\end{defn}

Definition from Neil Chue Hong:
\begin{defn}
Sustainable software is software which is:
-- Easy to evolve and maintain
-- Fulfils its intent over time
-- Survives uncertainty
-- Supports relevant concerns (Political, Economic, Social, Technical,
Legal, Environmental)~\cite{Katz2016}.
\end{defn}

Paper critical of a lack of a definition~\cite{VentersEtAl2014}.

@@

To achieve the qualities listed in Section~\ref{SecQualities}, the documentation
should achieve the qualities listed in this section.  All but the final quality
listed (abstraction), are adapted from the IEEE recommended practise for
producing good software requirements~\cite{IEEE1998}.  Abstraction means only
revealing relevant details, which in a requirements document means stating what
is to be achieved, but remaining silent on how it is to be achieved.
Abstraction is an important software development principle for dealing with
complexity~\cite[p.~40]{GhezziEtAl2003}.  Correctness was in the above list, so
it is not repeated here.  \citet{SmithAndKoothoor2016} present further details
on the qualities of documentation for SCS.

@@

Verifiability is related to testability, which is defined by McCall et al.\ as
``The effort required to test a program to ensure that it performs its intended
function'' \cite{VanVliet2000}.

@@

\begin{defn}
``An abstraction for a software artifact is a succinct description that suppresses
the details that are unimportant to a software developer and emphasizes the
information that is important.'' \cite{Krueger1992}
\end{defn}

\begin{defn}
``Abstraction means that we concentrate on the essential features and ignore,
abstract from, details that are not relevant at the level we are currently
working.''  \cite[p.\ 296]{VanVliet2000}
\end{defn}

>>>>

\begin{defn}
  A measure of the ease of installation.  \wss{Where does this definition come
    from? Please add a citation.  I believe it is from \citet{McCallEtAl1977},
    but you should verify this.}
\end{defn}

\begin{defn} \label{DefnInstallability}
  Installability is related to the amount of human effort required to install a
  software in a designated environment \citep{berander2005software}.
\end{defn}

\begin{defn}
  ``The capability of a software product to be installed in a specified
  environment'' \citep{berander2005software}.
\end{defn}

\begin{defn}
  ``The efficacy of the installation, uninstallation or reinstallation process
  of a software product in a specified environment'' (\citep{iso201017043})
\end{defn}

@@

The quality of a software's operation is dependent on the degree of correctness
\citep{berander2005software}. Correctness and reliability are said to have
dependencies, such that if a system exhibits a high degree of correctness then
it tends to be reliable (\citep{GhezziEtAl2003}).

@@

\begin{defn}
  A software is verifiable if its properties can be verified
  \citep{GhezziEtAl2003}.
\end{defn}

\begin{defn}
  Attributes of software that relate to the effort needed for validating the
  modified software \citep{berander2005software}.
\end{defn}

\begin{defn}
  The degree to which a system or component facilitates the establishment of
  test criteria and the performance of tests to determine whether those criteria
  have been met \citep{IEEEStdGlossarySET1990}.
\end{defn}

\begin{defn} \label{Defn_Verifiability1}
  The degree to which a requirement is stated in terms that permit establishment
  of test criteria and performance \citep{IEEEStdGlossarySET1990}.
\end{defn}

\begin{defn} \label{Defn_Verifiability2}
  Ease of performing testing on a software product or system
  \citep{IEEEStdGlossarySET1990}.
\end{defn}

@@

Verifiability involves ``solving the equations right'' \citep[p.~23]{Roache1998};
it benefits from rational documentation that systematically shows, with explicit
traceability, how the governing equations are transformed into code.
\oo{Verifiability is sometimes referred to as testability, so I culled some
  testability definitions here}

@@

\begin{defn}
  Validatability means ``solving the right equations'' \citep[p.~23]{Roache1998}.
  \oo{question about this definition}
\end{defn}

@@

\begin{defn}
  The probability that the software will operate as expected over a specified
  time interval (\citep{GhezziEtAl2003}).
\end{defn}

\begin{defn}
  A set of attributes that relate to the capability of software to maintain its
  level of performance under stated conditions for a stated period of time
  \citep{berander2005software}.
\end{defn}

\begin{defn}
  ``The capability of the software product to maintain a specified level of
  performance when used under specified conditions''
  \citep{international2001iso}.
\end{defn}

\begin{defn}
  Code possesses the characteristic reliability to the extent that it can be
  expected to perform its intended functions satisfactorily
  \citep{boehm2007software}.
\end{defn}

\begin{defn}
  A concern encompassing correctness and robustness \citep{meyer1988object}.
\end{defn}

@@

Reliability models can be used to predict reliability of a software product. For
example measuring Mean Time to Fail (MTTF) can be a good measure of reliability
\citep{berander2005software}.

@@

One core reference, for definitions and metrics, is
\citet{bevan1995measuring}.

@@

Section 11.2 of \citet{adams2015nonfunctional} does have a full definition.

@@

Reproducibility is a required component of the scientific
method \citep{Davison2012}.  Although QA has, ``a bad name among creative
scientists and engineers'' \citep[p.~352]{Roache1998}, the community need to
recognize that participating in QA management also improves reproducibility.
Reproducibility, like QA, benefits from a consistent and repeatable computing
environment, version control and separating code from
configuration/parameters \citep{Davison2012}.

@@

\begin{defn}
\noindent The ability to meet the needs of the present without compromising the ability of
future generations to meet their own needs \citep{Brundtland1987}.
\end{defn}

This is the definition used by \citet{IISD2019}.

To make it more useful, this definition is often split into three dimensions:
social, economic and environmental. \wss{cite UN paper [9] in
  \citet{PenzenstadlerAndHenning2013}}  To this list Penzenstadler and Henning
(2013) have added technical sustainability \citep{PenzenstadlerAndHenning2013}.
Where technical sustainability for software is defined as:

\begin{defn}
\noindent Technical sustainability has the central objective of long-time
usage of systems and their adequate evolution with changing surrounding
conditions and respective requirements \citep{PenzenstadlerAndHenning2013}.
\end{defn}

The fourth dimension of technical sustainability is also added
by \citep{WolframEtAl2017}.  Technical sustainability is the focus on the thesis
by \citet{Hygerth2016}.

\begin{defn}
  \noindent Sustainable development is a mindset (principles) and an
  accompanying set of practices that enable a team to achieve and maintain an
  optimal development pace indefinitely \citep{Tate2005}.
\end{defn}

Parnas discusses as software aging \citep{Parnas1994a}.

@@

\begin{defn}
  The concept of sustainability is based on three pillars: the
  ecological, the economical and the social. This means that for a software to
  be sustainable, we must take all of its effects -- direct and indirect -- on
  the environment, the economy and the society into account. In addition, the
  entire life cycle of a software has to be considered: from planning and
  conception to programming, distribution, installation, usage and
  disposal \citep{Heine2017}.
\end{defn}

\begin{defn}
  \noindent The capacity of the software to endure. In other words,
  sustainability means that the software will continue to be available in the
  future, on new platforms, meeting new needs \citep{Katz2016}.
\end{defn}

Definition from Neil Chue Hong:
\begin{defn}
Sustainable software is software which is:
-- Easy to evolve and maintain
-- Fulfils its intent over time
-- Survives uncertainty
-- Supports relevant concerns (Political, Economic, Social, Technical,
Legal, Environmental) \citep{Katz2016}.
\end{defn}

Paper critical of a lack of a definition \citep{VentersEtAl2014}.

@@

To achieve the qualities listed in Section~\ref{SecQualities}, the documentation
should achieve the qualities listed in this section.  All but the final quality
listed (abstraction), are adapted from the IEEE recommended practise for
producing good software requirements \citep{IEEE1998}.  Abstraction means only
revealing relevant details, which in a requirements document means stating what
is to be achieved, but remaining silent on how it is to be achieved.
Abstraction is an important software development principle for dealing with
complexity \citep[p.~40]{GhezziEtAl2003}.  Correctness was in the above list, so
it is not repeated here.  \citet{SmithAndKoothoor2016} present further details
on the qualities of documentation for SCS.

@@

Verifiability is related to testability, which is defined by McCall et al.\ as
``The effort required to test a program to ensure that it performs its intended
function'' \citep{VanVliet2000}.

@@

\begin{defn}
``An abstraction for a software artifact is a succinct description that suppresses
the details that are unimportant to a software developer and emphasizes the
information that is important.'' \citep{Krueger1992}
\end{defn}

\begin{defn}
``Abstraction means that we concentrate on the essential features and ignore,
abstract from, details that are not relevant at the level we are currently
working.''  \citep[p.\ 296]{VanVliet2000}
\end{defn}
